Foreign Exchange Speculation: An Event Study

### 2018-02-12 MDPI/MDPI_template/FinStudies3.tex
Completed third review.

\subsection{The Event Study}
An event study will be used to identify what happens to foreign exchange prices around the time that speculative sentiment or speculative positions are extreme.  If speculation is uninformed when speculative sentiment or speculative positions are extremely bias to one direction, there should be the greatest divergence from fundamental value and therefore the greatest risk of reversal; if speculation is informed these extremes are part of the adjustment to a new equilibrium.  An event study will analyse the performance of security of asset prices around an event.  In this case the event is the extreme of speculative sentiment or extreme speculative activity.

>>>>

\subsection{The Event Study}
It is common to use series that measure market sentiment or market postitions or even proxies like moving averages as \emph{trading-rules} that aim to achieve abnormal returns.  See for example, \citet{Olson}, \citet{ImprovedMA}, \citet{Malz2} and \citet{DeBrock}.  It is assumed that the signals will identify times when the market is inefficient.  However, in our case there is a direct test of the informational content of extreme speculative sentiment and speculative positions.    A special case of the event study method will be used to identify what happens to foreign exchange prices around the time that speculative sentiment or speculative positions are extreme.   If speculation is uninformed when speculative sentiment or speculative positions are extremely bias to one direction, there should be the greatest divergence from fundamental value and therefore the greatest risk of reversal; if speculation is informed these extremes are part of the adjustment to a new equilibrium.  An event study will analyse the performance of security of asset prices around an event.  In this case the event is the extreme of speculative sentiment or extreme speculative activity.
